---
title: "BGFRA"
author: "Francisco Javier Luna-Vázquez"
date: "`r format(Sys.Date())`"
output: github_document
---

Bayesian Genomic Functional Regression Analysis in R

## Instructions for proper implementation

### Installation

To complete installation of dev version of BGFRA from GitHub, you have to install a few packages first.

```{r installation, eval = FALSE}
install.packages('devtools')
devtools::install_github('frahik/BGFRA')
```

### Quick use 

#### Load data

```{r loadData}
rm(list = ls())
library(BGFRA)
data("wheat_BGFRA")

data <- Wheat # Load from data wheat_BGFRA
Bands <- Bands # Load from data wheat_BGFRA
Wavelengths <- Wavelengths # Load from data wheat_BGFRA

## Linear predictor
ETA2 <- list(Env = list(X = model.matrix(~0+as.factor(data$Env)), model = "FIXED"),
             Line = list(X = model.matrix(~0+as.factor(data$Line)), model = "BRR"),
             Bands = list(X = Fourier.Basis(Bands, Wavelengths, n.basis = 21, interaction = NULL), model = "BRR")
)
```

#### Fit model

```{r fitModel}
fm2 <- BGFRA(data, ETA = ETA2, nIter = 1000, burnIn = 300)
summary(fm2)
plot(fm2)
```

### Cross-validation model

```{r CVModel}
pm2 <- BGFRA(data, ETA = ETA2, nIter = 1000, burnIn = 300, folds = 5, set_seed =10)
pm2$results
boxplot(pm2)
```

### Params

In progress

## Advanced demos


## Citation

How to cite the package...

## Authors

Francisco Javier Luna-Vázquez (Author, Maintainer)

Osval Antonio Montesinos-López (Author)
