---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Loading library

```{r}
library(GFR)
```


## Bayesian Functional regression with three environments using Wheat_GFR data

To load the data, whe use the `data()` function,
```{r}
data('Wheat_GFR')
```

Also, we use the `ETAGenerate()` function to create the linear predictor, this linear predictor will be representended like this.

$$
\eta = Env + Line + Env \times Line + Bands 
$$
```{r}
ETA1 <- ETAGenerate(Wheat_GFR, basisType = 'Fourier.Basis', Bands = Wheat_Bands, Wavelengths = Wheat_Wavelengths, priorType = 'BayesA', method = 'Alternative2', nBasis = 21)
```

If we want to fit the model, we can use the `BFR()` function

```{r}
FM1 <- BFR(Wheat_GFR, ETA = ETA1, nIter = 1500, burnIn = 1000)
```

In this example, we use 1500 iterations only to show,

```{r}
CrossV <- list(Type = 'KFold', nFolds = 3)
PM1 <- BFR(ETA = ETA1, nIter = 1500, burnIn = 1000, CrossValidation = CrossV, set_seed = 10)
summary(PM1)
plot(PM1)
boxplot(PM1)
```


## Bayesian Functional regression with three environments using Wheat_GFR data

```{r}
ETA3 <- list(Env = list(X = model.matrix(~0+as.factor(Wheat_GFR$Env)), model = 'FIXED'),
             Line = list(X = model.matrix(~0+as.factor(Wheat_GFR$Line)), model = 'BRR'),
             Bands = list(X = Bspline.Basis(Wheat_Bands, Wheat_Wavelengths, nBasis = 23), model = 'BayesA'))
```

```{r}
FM2 <- BFR(Wheat_GFR, ETA = ETA3, nIter = 15000, burnIn = 10000, CrossValidation = CrossV, set_seed = 10)
```


```{r}
CrossV <- list(Type = 'KFold', nFolds = 5)

PM2 <- BFR(Wheat_GFR, ETA = ETA3, nIter = 15000, burnIn = 10000, CrossValidation = CrossV, set_seed = 10)
plot(PM2, select = 'MSEP')
boxplot(PM2, select = 'MSEP')
```

#Clean the directory
```{r}
cleanDat(forceClean = T)
```

