---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Esta función ha sido diseñada para ser utilizada entre las dos versiones del ajuste de los modelos previstos, modelos bayesianos y modelos frequentistas, 

the full list of parameters are the following,
```{r, eval=FALSE}
ETAGenerate(dataset, datasetID = 'Line', Multivariate = 'Traditional', GenomicMatrix = NULL, REML= NULL, priorType = 'BRR', Bands = NULL, Wavelengths = NULL, method = 'Simple', basisType = 'Fourier.Basis', nBasis = 1, ...)
```

and the description of each, is the next:

- dataset: It's the dataset with the available data of the Environments, Traits, Lines and the Response.
- datasetID: It's the identificator column to use in the $\beta_{Line}$
- Multivariate: It's the way to solve the Multi-Trait and Multi-Environment predictors, by default it's by the `Traditional` way, but also we can use the method propoused by Montesinos-López et. al. (2018) in <doi: >, see the next section.
- GenomicMatrix: It's the GenomicMatrix.
- REML: Frequentist methods, by default is NULL , else if is FALSE, else is TRUE.
- priorType: Bayesian priors.
- Bands: Bands.
- Wavelengths: name of the bands.
- method: method to apply the basis.
- basisType: ways.
- nBasis: Number of basis ot generate.


## Bayesian ETA made with ETAGenerator

To do analysis with bayesian methods, the `ETAGenerate()` function can be reduced to the following parameters.

```{r, eval=FALSE}
ETAGenerate(dataset, datasetID = 'Line', Multivariate = 'Traditional', GenomicMatrix = NULL, priorType = 'BRR', Bands = NULL, Wavelengths = NULL, method = 'Simple', basisType = 'Fourier.Basis', nBasis = 1, ...)
```


The `ETAGenerator()` function can generate the next eight tipes of linear predictors,

$$
\begin{align}
  \eta_{Single}       &= \\
  \eta_{SingleBands}  &= Bands\\
  \eta_{Env}          &= Env + Line + Line \times Env\\
  \eta_{EnvBands}     &= Env + Line + Line \times Env + Bands\\
  \eta_{Trait}        &= Trait + Line + Line \times Trait\\
  \eta_{TraitBands}   &= Trait + Line + Line \times Trait + Bands\\
  \eta_{Multi}              &= Env + Trait + Line + Line \times Env + Line \times Trait + Env \times Trait+ Env \times Trait \times Line\\
  \eta_{MultiBands}   &= Env + Trait + Line + Line \times Env + Line \times Trait + Env \times Trait+ Env \times Trait \times Line + Bands\\
\end{align}
$$

### Priors

Where it can be adjusted with a prior `FIXED`, `BRR`, `BayesA`, `BayesB`, `BayesC`, `BL` or `RKHS` (for kernels),  the function autodetects when the prior specified by the user can be used, or can change by one of the rest, commonly when the number of environments or traits are less than 10 the prior assigned by the function for this predictors is `FIXED`, also when a `GenomicMatrix` is used, the `Line` predictor will use `RKHS` method.   

### Modifying Bands
When a Bands are provided, the parameter `method` indicate how to solve the basis,
$$
\begin{align}
  Simple        &= Bands\\
  Conventional  &= \int_i^j Bands\\
  Alternative   &= \phi I \phi^t \int_i^j Bands  \\
  Alternative2  &= \phi \int_i^j Bands
\end{align}
$$

### Multivariate SVD and Traditional

By default the function prepares the data to solve it by the traditional way, but it's possible and neccesary modify this adjust when a heavy data Multi-Trait & Multi-Environment model it's present, this solution named `SVD` can be used specifying in the `Multivariate` parameter, and the full description of this can be found in <doi: >

## Bayesian Handmade ETA
For more experimented users, all of this modifications can be adjusted manually, incluse add or extend to new alternative ways or models to generate the linear predictor, supose that need want the next eta,
$$
\eta = Env + Lines 
$$
And this predictor it's not available in the `ETAGenerator()` function, así que necesitamos crearla de manera manual, se podría decir que este paso es para personas con un conocimiento avanzado


## Frequentist ETA made with ETAGenerator

```{r, eval=FALSE} 
ETAGenerate(dataset, datasetID = 'Line', GenomicMatrix = NULL, REML= NULL, Bands = NULL, Wavelengths = NULL, method = 'Simple', basisType = 'Fourier.Basis', nBasis = 1, ...)
```

When the predictions or the adjust of the model that we need it's with the frequentist statitistical methods, we can specified with the `REML` method, by default is NULL, to adjust with the Bayesian methods, but if it's `FALSE` the model propoused it's with the model or if it's `TRUE` the model propused it's,

## Frequentist Handmade ETA

For more experimented users, all of this modifications can be adjusted manually.
